Title here

### 2016-12-14 portfolio/text/ms.Rmd
Add effort fig

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort, specializing tends to be
associated with increased revenue (Fig. \ref{fig:within}; Fig. S\ref{fig:fe},
Fig. S\ref{fig:re}). On average, there is a ~0.5% increase in the year-to-year
revenue ratio per 1% decrease in species diversity, and across strategies, `r
g2_dens`% of the probability density supports a positive relationship between
specialization and revenue. The converse is also usually true --- generalizing
tends to be associated with lower expected revenue after accounting for fishing
effort (i.e. Fig. S\ref{fig:mirror}A and S\ref{fig:mirror}B are near mirror
images left to right). This benefit of specializing is only apparent after
accounting for fishing effort. Given that fishing for more species tends to be
associated with increased fishing effort (fishing more days), generalizing tends
to be associated with higher revenue when not standardizing for days finished
(Fig. S-TODO).

>>>>

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort, specializing tends to be
associated with increased revenue (Fig. \ref{fig:within}; Fig. S\ref{fig:fe},
Fig. S\ref{fig:re}). On average, there is a ~0.5% increase in the year-to-year
revenue ratio per 1% decrease in species diversity, and across strategies, `r
g2_dens`% of the probability density supports a positive relationship between
specialization and revenue. The converse is also usually true --- generalizing
tends to be associated with lower expected revenue after accounting for fishing
effort (i.e. Fig. S\ref{fig:mirror}A and S\ref{fig:mirror}B are near mirror
images left to right). This benefit of specializing is most apparent after
accounting for fishing effort. Given that fishing for more species tends to be
associated with increased fishing effort (fishing more days), specializing tends
to be ...TODO (Fig. S\ref{fig:noeffort}).
